\subsection{Python Module}
\label{sec:python-module}

The core functionality of the \textbf{VEIN} system is implemented via the \texttt{vein.Solver}, an extension of
the \texttt{z3.Solver} class offered in the Z3 Python
package\footnote{\href{https://pypi.org/project/z3-solver}{\textbf{PyPi package}}}. This design choice
ensures flexibility and ease of use for researchers already familiar with using the Z3 Python API.

The methods offered by \texttt{vein.Solver} are:
\begin{itemize}
	\item \texttt{load\_onnx}: loads a neural network in ONNX file format.
	\item \texttt{load\_smtlib}: loads a file containing the specification.
	\item \texttt{check}: orchestrates the translation and reduction pipeline before invoking the
		solver to check the specification against one or many neural networks.
\end{itemize}

The framework uses a \textit{lazy evaluation} strategy: when loading a neural network, it is placed
into a pending queue and it is reduced to normal form only after the \texttt{check} method is
called.

The specification follows the SMT-LIB\footnote{\href{https://smt-lib.org}{\textbf{SMT-LIB Website}}}
format. It should contain the input and output symbolic variables declarations, optional range
constraints on the input variables and the properties to be verified. For Multi-Network (relational)
verification, the system ensures that multiple networks share the same input symbolic variables.
This approach allows Z3 to compare their outputs directly given the same inputs.

The execution pipeline is implemented within the \texttt{check} method:
\begin{itemize}
	\item \texttt{inpla\_export}: invokes the translation layer to generate an IN.
	\item \texttt{inpla\_run}: executes INPLA as a subprocess.
	\item \texttt{z3\_evaluate}: parses the normal form, represented by an AST, and constructs the
		Z3 expression.
\end{itemize}
This method utilizes a memoization technique to increase performance: if a specific pair of (neural
network, range constraints) has been previously reduced to a normal form, the system retrieves the
cached Z3 expression, instead of running the pipeline redundantly.
